---
title: "Revenue Use and Public Support for A Carbon Tax"
author: |
  | \textbf{\large{Matthew C. Nowlin}}
  | \textit{College of Charleston}
  | \textbf{\large{Kuhika Gupta and Joseph Ripberger}}
  | \textit{University of Oklahoma}
institute: American Political Science Association 
date: August 2019
bibliography: /Users/nowlinmc/Dropbox/refs.bib
output:
  beamer_presentation:
    keep_tex: yes
    theme: "metropolis"
    slide_level: 2
    fig_crop: false 
    fig_caption: false
    includes:
      in_header: /Users/nowlinmc/Dropbox/Projects/Manuscripts/beamerPackages.txt
header-includes: 
- \setbeamertemplate{page number in head/foot}[default]
---


```{r setup, include=FALSE, message=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

```{r, include=FALSE, message=FALSE}
source("scripts/data-recodes.R")
library(tidyverse)
library(dotwhisker)
library(broom)

treat <- table(CTdata$treatment)
as.vector(treat)
```

## Carbon Tax  


\large 

**Carbon pricing is generally seen by economists and others as the most efficient and effective set of climate mitigation policies**

\vspace{0.25in}
But, low levels of public support for carbon pricing [@carattiniOvercomingPublicResistance2018]

* Some increase with funds being used for renewable energy [@kotchenPublicWillingnessPay2017; @amdurPublicViewsCarbon2014]

* Some increase with a tax rebate [@carattiniHowWinPublic2019]

# Does revenue use influence public support for a carbon tax?  

---

## Analysis 

\large

**We leverage a survey experiment to examine support for a carbon tax** 

* Overall support, pre-and-post revenue use treatments 

* Ranking of revenue uses post treatment 

* Relative support for a carbon compared to others climate policies 

* Subset analysis for ideology and partisanship 



## Hypotheses

**Support**

* More support when tax is used for _renewable energy_ or a _tax rebate_
* More support when tax is used for _deficit reduction_ or a _tax rebate_ for _conservatives_ and _Republicans_  

**Revenue ranking** 

* Ranking of revenue use responsive to experimental condition

**Relative support**

* Increase in ranking when tax is used for _renewable energy_ or a _tax rebate_ 
* Increase in  ranking when tax is used for _deficit reduction_ or a _tax rebate_ for _conservatives_ and _Republicans_  

---

## Data 

\large 

**Nationally representative sample obtained through Qualtrics**  

**Quotas for age, gender, race/ethnicity** 

**Survey administered through Qualtrics**

**N = `r nrow(CTdata)` ** 


## Survey Experiment 

**Respondents were presented with a prompt about a carbon tax, including pro and con arguments** 

**Randomly assigned to one of five tracks**: 

* **General Fund** (n=`r treat[length(treat)-3]`)
* **Reduce Budget Deficit** (n=`r treat[length(treat)-2]`)
* **Renewable Technology** (n=`r treat[length(treat)-1]`)
* **Tax Rebate** (n=`r treat[length(treat)]`)
* **Control** (n=`r treat[length(treat)-4]`)

Carbon tax support pre-treatment (1 to 7 scale): m = `r round(mean(CTdata$pre_support, na.rm=TRUE),2)`

Post-treatment support: `r round(mean(CTdata$post_support, na.rm=TRUE),3)`

## Results: Support  

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/model.png}
\end{figure}

## Results: Support by Political Beliefs 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/ideology-model.png}
\end{figure}

## Results: Support by Political Beliefs 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/partisan-model.png}
\end{figure}

## Results: Revenue Use 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/rev-rank-graph.png}
\end{figure}

## Results: Revenue Use 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/refund-rank-model.png}
\end{figure}

## Results: Revenue Use 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/renew-rank-model.png}
\end{figure}

## Results: Revenue Use 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/deficit-rank-model.png}
\end{figure}

## Results: Revenue Use 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/fund-rank-model.png}
\end{figure}

## Results: Climate Policy Rankings 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/rank-graph.png}
\end{figure}

## Results: Carbon Tax Ranking

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/rank-model.png}
\end{figure}

## Results: Carbon Tax Ranking by Political Beliefs 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/ideology-rank-model.png}
\end{figure}

## Results: Carbon Tax Ranking by Political Beliefs 

\begin{figure}
\includegraphics[width = 4in, height= 3in]{../fig-output/partisan-rank-model.png}
\end{figure}

## Conclusion 

**Revenue use can shift support** 

* Tax rebate 

* Tax rebate, deficit reduction for conservatives and Republicans 

**Trade-offs between tax refund and renewable energy investment**  

**Carbon pricing still unpopular relative to other policy options**   

* Tax rebate does shift relative support 

 

## References 
